Getting Started with Kaggle Competition
========================================================

After downloading the .csv files, we load the data as usual.

```{r}
# Change this to your data directory
data.dir <- "/Users/blancavillanueva/Dropbox/_a1516/stats202/kaggle1"
setwd(data.dir)
# Read in each data files into a data frame
training.target <- read.csv("training_target.csv")
training.features <- read.csv("training_features.csv")
validation.features <- read.csv("validation_features.csv")
validation.target <- read.csv("validation_target.csv")
leaderboard.features<- read.csv("leaderboard_features.csv")
```

Let's take a look at the format of **training.target** data:

```{r}
head(training.target)
```

We also load the **leaderboard_predictions-example.csv** file to see the output format. 

```{r}
leaderboard.predictions <- read.csv("leaderboard_predictions-example.csv") 
head(leaderboard.predictions)
```
The format matches with the **training.target**. 

Here, for each leaderboard subject, let's predict the target by the mean of the training target.

```{r}
library(glmnet)
y <- training.target$ALSFRS_slope
y.test <- validation.target$ALSFRS_slope

df <- data.frame(merge(training.features, training.target, by = 'subject.id'))
df.test <- data.frame(merge(validation.features, validation.target, by = 'subject.id'))

for(i in 1:ncol(df)){
  df[is.na(df[,i]), i] <- mean(df[,i], na.rm = TRUE)
}

for(i in 1:ncol(df.test)){
  df.test[is.na(df.test[,i]), i] <- mean(df.test[,i], na.rm = TRUE)
}

# if there are remaining NA values, use means from training set
for(i in 1:ncol(df.test)){
  df.test[is.na(df.test[,i]), i] <- mean(df[,i], na.rm = TRUE)
}

for(i in 1:ncol(leaderboard.features)){
  leaderboard.features[is.na(leaderboard.features[,i]), i] <- mean(leaderboard.features[,i], na.rm = TRUE)
}

# if there are remaining NA values, use mean from training + validation set
joined.df = rbind(df, df.test)
for(i in 1:ncol(leaderboard.features)){
  leaderboard.features[is.na(leaderboard.features[,i]), i] <- mean(joined.df[,i], na.rm = TRUE)
}

# x = model.matrix(ALSFRS_slope~., df)[,-1]
# x.test = model.matrix(ALSFRS_slope~., df.test)[,-1]

# cv.lasso <- cv.glmnet(x, y)
# coef(cv.lasso, s = "lambda.1se")
# opt.lambda = cv.lasso$lambda.1se

x.leaderboard = as.matrix(leaderboard.features)
# lasso.pred = predict(cv.lasso, s=cv.lasso$lambda.1se, newx=x.leaderboard)
# mean((lasso.pred-y.test)^2)
# leaderboard.predictions$ALSFRS_slope <- lasso.pred

# Random Forest
rf.als = randomForest(ALSFRS_slope~., data=df, importance=TRUE, na.action=na.roughfix)
yhat.rf = predict(rf.als, newdata=x.leaderboard)
leaderboard.predictions$ALSFRS_slope <- yhat.rf
```

We use **write.csv** function to write a CSV file in the contest format with the leaderboard subject predictions. 

```{r}
write.csv(leaderboard.predictions, file = "leaderboard_predictions_rf1.csv",row.names=FALSE)
```
